---
title: "Final Part 2"
format: html
---

For this part of the final I am providing you with some data and you need to fit a prediction model. I have some held out test data that I will evaluate your prediction model with. You will upload two things into Canvas for this part: (A) this .html file and (B) A final_mod.rds file that you will save (see below) that contains the final model that you fit (that I will run on my test data).



```{r}
library(tidyverse)
library(tidymodels)
```

## Read in the data

Here we have a dataset with 12 predictors, `x1` through `x12`, and an outcome, `y`. Running the code below will read the data into your session.

```{r}
#| label: load-data
load("data.rds")
```

## Build a prediction model

Using any of the techniques we learned in class, build a prediction model predicting `y` from any of the remaining variables. Be sure to complete any necessary pre-processing.


```{r}
#| label: prediction-model


```

## Final model object

When you have finished building your model, save the **final model object** as `final_mod`. This object should either be the output from using the `fit()` function on your finalized workflow *or* a model stack from an ensemble method. Be sure to save your final model to upload to canvas by running the save function as below.

```{r}
#| label: final-mod

# Update the line below and save your final model object. Make sure that it "works"
# by running the check (that is, make sure that it is an object that you can predict from)

final_mod <- ----

## check that final_mod works
final_mod |>
  predict(data) |>
  bind_cols(data) |>
  rmse(estimate = .pred, truth = y)

## Save your final model to upload to canvas
save(final_mod, "final_mod.rds")
```

